Empty Homes V1

### 2017-05-08 CreateExcelTemplates.Rmd
Extra Boroughs and changed templates

@@

This chunk checks the exiatane of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup. Creating the lookup takes quite a lot of time so it is good to only have to do it once.
```{r}

@@

    PstCdLSOA.filt <- PstCdLSOA.Reg %>% filter(LAD15NM == LAD)
    print(paste(n, ":", LAD))
      ExemptionsFile <- paste0(LAD,"ExemptionsLSOA.xlsx")
      CTBandsFile <- paste0(LAD,"CTBandsLSOA.xlsx")
      setwd(basewd)
      wb <- loadWorkbook("Convert Postcode to LSOA.xlsx")
      #input the LSOA lookup table
      writeData(wb, sheet = "LSOAdata", PstCdLSOA.filt, colNames = T)
      #add in randomly sampled postcodes as an example
      writeData(wb, sheet = "Input", sample(PstCdLSOA.filt$Postcode, 6),
                startCol = 2, startRow = 2,
                colNames = F)
      setwd(file.path(Regions, title))
      saveWorkbook(wb,ExemptionsFile ,overwrite = T)
      saveWorkbook(wb,CTBandsFile ,overwrite = T)
    })
})

>>>>

#These three blocks are all you need to to generate the templates... I think it needs to be checked when the packages have updated

@@

This chunk checks the existance of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup. Creating the lookup takes quite a lot of time so it is good to only have to do it once.
```{r}

@@

    PstCdLSOA.filt <- PstCdLSOA.Reg %>% filter(LAD15NM == LAD)
    print(paste(n, ":", LAD))
      ExemptionsFile <- paste0(LAD,"ExemptionsLSOA.xlsx")
      DiscountsFile <- paste0(LAD,"DiscountsLSOA.xlsx")
      setwd(basewd)
      wb <- loadWorkbook("Convert Postcode to LSOA.xlsx")
      #input the LSOA lookup table
      writeData(wb, sheet = "LSOAdata", PstCdLSOA.filt, colNames = T)
      #add in randomly sampled postcodes as an example
      writeData(wb, sheet = "Input", sample(PstCdLSOA.filt$Postcode, 6),
                startCol = 2, startRow = 2,
                colNames = F)
      setwd(file.path(Regions, title))
      saveWorkbook(wb,ExemptionsFile ,overwrite = T)
      writeData(wb, "Input", "Discount_Class") #So that it says Discounts not exemptions, so nobody gets confused.
      saveWorkbook(wb,DiscountsFile ,overwrite = T)
    })
})

### 2017-05-08 EmptyHomesV1.Rmd
Extra Boroughs and changed templates

# Using the semi data

@@

@@

#ward folder
setwd(SemiLondon)
list.files()

@@

#Chelsea
Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM))

Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
  mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(X.Ward) %>%
  mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related., Empty..50..premium., Moorings , na.rm = TRUE),
         LowUse = Empty + Second.Homes) %>% ungroup

Chelsea[is.na(Chelsea)] <-0
rm(Chelwards)

Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
  mutate(LowUsePerc = LowUse/WardHomes)

cor(Chel2$PrimePerc, Chel2$LowUsePerc)
cor(Chel2$MeanPrice, Chel2$LowUsePerc)

Chel2 %>%
  mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>% 
  ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() + 
  geom_smooth(method ="lm", se = FALSE) +
  labs(title = "Relationship between % of Prime Sales and % Low Use", 
       x = "% of properties sold in 2016 over £1M by electoral ward",
       y = "% of properties either empty or second homes") +
  theme(plot.title = element_text(hjust = 0.5))  +
  coord_cartesian(xlim = c(15,78), expand = TRUE)

@@

#Merton
wardnames %>% filter(LAD11NM == "Merton")
Merton <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X) %>%
  filter(X != "Norbury", X!="Nightingale", X !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home )

@@

Kingston <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..)

@@

#Greenwhich
list.files()
wardnames %>% filter(grepl("Greenwich", LAD11NM))

Greenwich <- read_excel( "FOI-3348 ctfoi35report.xlsx" ) %>%  
  setNames(make.names(names(.))) %>%
  filter(grepl("EMPTY",Exempt.Discount.Description)) %>% 
  select(-Exempt.Code) %>%
  spread(key= Exempt.Discount.Description, value = Total, fill = 0) %>%
  mutate(Empty = rowSums(.[,-1]), LowUse = Empty) %>%
   bind_cols(., wardnames %>% filter(grepl("Greenwich", LAD11NM)))

@@

Plot Map
```{r}
AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
                 SOUDAT, KINDAT, TOWDAT, GREDAT, CAMDAT, 
                 BRODAT, HARDAT, RICDAT, HILDAT, BEXDAT,
                 SUTDAT) %>% 
  mutate(LowUsePerc = LowUse/WardHomes, 
         EmptyPerc = Empty/WardHomes,
         EmptyPercRank = percent_rank(Empty/WardHomes))

@@

#SIngle borough detail
SUTDAT %>%
  mutate(LowUsePerc = LowUse/Homes, 
         EmptyPerc = Empty/Homes,
         EmptyPercRank = percent_rank(Empty/Homes)) %>%
ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  ggtitle("Kensington and Chelsea ward level % low use") + 
  theme(plot.title = element_text(hjust = 0.5))
```

@@

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
             x = 0.35 , y = 7.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)

>>>>

# Using the full data

@@

#Islington

Islington <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4] %>% setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,-c(1,12,13)]), Empty = LowUse ) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

ISL2 <- Islington %>% mutate(LowUsePerc = LowUse/Homes)

ISLDAT <- AG %>% filter(LAD11NM == "Islington") %>% 
  left_join(., select(Islington, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Greenwhich
list.files()
wardnames %>% filter(grepl("city", LAD11NM))

Greenwich <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% ungroup %>%
  mutate(Exemption.type = trimws(Exemption.type))  %>%
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,c(2,3,4,21,22)]), Empty = LowUse -  EMPTY.CLASS.B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

Greenwhich2 <- Greenwich %>% mutate(LowUsePerc = signif(LowUse/Homes*100,3))

@@

#RBKC

Chelsea <- read.xlsx( "Kensington and ChelseaDiscountsLSOA.xlsx" , colNames = TRUE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

#Barking
Bark <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colNames = FALSE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2,3,6,7)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BARKDAT <- AG %>% filter(LAD11NM == "Barking and Dagenham") %>% 
  left_join(., select(Bark, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Barnet

Barnet <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2:8)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Newham

Newham <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Semi data 
```{r}
#ward folder
setwd(SemiLondon)
list.files()

@@

#Chelsea
# Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM)) 
# 
# Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(X.Ward) %>%
#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related., Empty..50..premium., Moorings , na.rm = TRUE),
#          LowUse = Empty + Second.Homes) %>% ungroup
# 
# Chelsea[is.na(Chelsea)] <-0
# rm(Chelwards)
# 
# Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
#   mutate(LowUsePerc = LowUse/WardHomes)
# 
# cor(Chel2$PrimePerc, Chel2$LowUsePerc)
# cor(Chel2$MeanPrice, Chel2$LowUsePerc)
# 
# Chel2 %>%
#   mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>% 
#   ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() + 
#   geom_smooth(method ="lm", se = FALSE) +
#   labs(title = "Relationship between % of Prime Sales and % Low Use", 
#        x = "% of properties sold in 2016 over £1M by electoral ward",
#        y = "% of properties either empty or second homes") +
#   theme(plot.title = element_text(hjust = 0.5))  +
#   coord_cartesian(xlim = c(15,78), expand = TRUE)
#  
# 
# 
# CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
#   filter(WD16NM!= "Kensal Green")

@@

#Merton
wardnames %>% filter(LAD11NM == "Merton")
Merton <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home )

@@

Kingston <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..)

@@

#Havering Is census wards not electoral ones
# test <- wardnames %>% filter(grepl("Havering", LAD11NM))
# 
# Havering <- read.xlsx("Havering1.xlsx")[,-2] %>% gather(key = "Ward", value = "counts",-X1) %>%
#   mutate(X1 = make.names(X1)) %>%
#   spread(key = "X1", value = "counts", fill = 0)

@@

Plot Map
```{r}
AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
                 SOUDAT, KINDAT, TOWDAT, GREDAT, CAMDAT, 
                 BRODAT, HARDAT, RICDAT, HILDAT, BEXDAT,
                 SUTDAT, ISLDAT, BARKDAT, BARNDAT) %>% 
  mutate(LowUsePerc = LowUse/WardHomes*100, 
         EmptyPerc = Empty/WardHomes*100,
         EmptyPercRank = percent_rank(Empty/WardHomes))

@@

ggplotly() #STFD!
#Single borough detail

AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
  left_join(., select(Chelsea, LSOA_CODE, LowUse, Empty, Homes), by = c("lsoa11cd"="LSOA_CODE")) %>% 
  ungroup %>%
  filter(WD16NM!= "Kensal Green") %>%
  mutate(LowUsePerc = LowUse/Homes.y*100, 
         EmptyPerc = Empty/Homes.y*100,
         EmptyPercRank = percent_rank(Empty/Homes.y)) %>%
ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())+ 
  scale_fill_continuous(name = "Percentage")+
  ggtitle("Islington Exemptions")

Bourough2 <- Chelsea %>% ungroup %>% mutate(LowUsePerc = LowUse/Homes, 
         EmptyPerc = Empty/Homes,
         EmptyPercRank = percent_rank(Empty/Homes))

@@

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
             x = 0.35 , y = 2.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)
